Metric Principle Component Analysis: \\ On Identifying Important Subspaces for Approximation

### 2020-08-22 [2018-10]_(metric_PCA)/paper.tex
Found issue in last table where accuracies were flipped, should have been one minus the values shown.

\begin{table}
  \centering
  \renewcommand{\arraystretch}{1.2}
  \begin{tabular}{c c c c c}
    \hline
    \textbf{Data Set} & \textbf{Approximator}
      & \multiline{\textbf{Reduction}\\[-1mm]\textbf{Technique}}
      & \multiline{\textbf{Reduced}\\[-1mm]\textbf{Dimension}}
      & \multiline{\textbf{Lowest}\\[-1mm]\textbf{Mean}\\[-1mm]\textbf{Error}} \\
    \hline \hline
    \multirow{5}{*}{\textit{Yelp}}
    & Delaunay & PCA & 21 & 0.512 \\
    & KNN (1) & MPCA & 6 & 0.610 \\
    & KNN (10) & PCA & 6 & \underline{0.493} \\
    & LSHEP & raw & 63 & 0.678 \\
    & MLPRegressor & PCA & 1 & 0.515 \\
    \hline
    \multirow{5}{*}{\textit{MNIST}}
    & Delaunay & PCA & 8 & 0.132 \\
    & KNN (1) & MPCA & 78 & \underline{0.046} \\
    & KNN (10) & MPCA & 78 & 0.051 \\
    & LSHEP & PCA & 8 & 0.139 \\
    & MLPRegressor & PCA & 261 & 0.133 \\
    \hline
    \multirow{5}{*}{\textit{CIFAR10}}
    & Delaunay & PCA & 31 & \underline{0.631} \\
    & KNN (1) & MPCA & 31 & 0.681 \\
    & KNN (10) & MPCA & 31 & 0.643 \\
    & LSHEP & PCA & 31 & 0.650 \\
    & MLPRegressor & raw & 3072 & 0.897 \\
    \hline
  \end{tabular}
  \vspace{5mm}
  \caption{In this expanded set of results, the optimal reduction
    technique and subspace size is presented for each algorithm and
    for each real approximation problem. Notice that MPCA is not the
    most common \textit{best} reduction technique, which is
    counterintuitive. This suggests that the data provided for each
    approximation problem is in fact representative of the underlying
    phenomenon being modeled. It also suggests that the noise
    introduced in randomly sampling pairwise vectors for MPCA may
    inhibit its performance on approximation problems that are
    well-represented by available data.}
  \label{tab:all-results}
\end{table}

>>>>

\begin{table}
  \centering
  \renewcommand{\arraystretch}{1.2}
  \begin{tabular}{c c c c c}
    \hline
    \textbf{Data Set} & \textbf{Approximator}
      & \multiline{\textbf{Reduction}\\[-1mm]\textbf{Technique}}
      & \multiline{\textbf{Reduced}\\[-1mm]\textbf{Dimension}}
      & \multiline{\textbf{Lowest}\\[-1mm]\textbf{Mean}\\[-1mm]\textbf{Error}} \\
    \hline \hline
    \multirow{5}{*}{\textit{Yelp}}
    & Delaunay & PCA & 21 & 0.512 \\
    & KNN (1) & MPCA & 6 & 0.610 \\
    & KNN (10) & PCA & 6 & \underline{0.493} \\
    & LSHEP & raw & 63 & 0.678 \\
    & MLPRegressor & PCA & 1 & 0.515 \\
    \hline
    \multirow{5}{*}{\textit{MNIST}}
    & Delaunay & PCA & 8 & 0.132 \\
    & KNN (1) & MPCA & 78 & \underline{0.046} \\
    & KNN (10) & MPCA & 78 & 0.051 \\
    & LSHEP & PCA & 8 & 0.139 \\
    & MLPRegressor & PCA & 261 & 0.133 \\
    \hline
    \multirow{5}{*}{\textit{CIFAR10}}
    & Delaunay & PCA & 31 & 0.369 \\
    & KNN (1) & MPCA & 31 & 0.319 \\
    & KNN (10) & MPCA & 31 & 0.357 \\
    & LSHEP & PCA & 31 & 0.350 \\
    & MLPRegressor & raw & 3072 & \underline{0.103} \\
    \hline
  \end{tabular}
  \vspace{5mm}
  \caption{In this expanded set of results, the optimal reduction
    technique and subspace size is presented for each algorithm and
    for each real approximation problem. Notice that MPCA is not the
    most common \textit{best} reduction technique, which is
    counterintuitive. This suggests that the data provided for each
    approximation problem is in fact representative of the underlying
    phenomenon being modeled. It also suggests that the noise
    introduced in randomly sampling pairwise vectors for MPCA may
    inhibit its performance on approximation problems that are
    well-represented by available data.}
  \label{tab:all-results}
\end{table}
